\documentclass[11pt,fleqn]{exam}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fancyvrb}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{algpseudocode}
\usepackage{comment}
\usepackage{enumitem}
\usepackage[margin=0.75in]{geometry}
\usepackage{tikz}
\usetikzlibrary{arrows,arrows.meta,positioning,intersections,shapes.gates.logic.US,calc}
\algnewcommand\algorithmicforeach{\textbf{for each}}
\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
\newcommand{\fillinMCmath}[1]{\begin{tikzpicture}\draw circle [radius=0.5em];\end{tikzpicture}\ #1}
\newcommand{\fillinMCmathsoln}[1]{\begin{tikzpicture}\draw[black, fill=blue] circle [radius=0.5em];\end{tikzpicture}\ #1}
\newcommand{\ptsamt}[1]{[#1~points]}
\newcommand{\ptamt}[1]{[#1~point]}

%%% Adding Colour to Questions and Answers
\usepackage{color}

\definecolor{solnblue}{rgb}{0,0,1}
\newenvironment{soln}{\color{solnblue}}{}

%Questions

% Answers
\definecolor{blu}{rgb}{0,0,0.5}
\def\blu#1{{\color{blu}#1}}
\definecolor{gre}{rgb}{0,.3,0}
\def\gre#1{{\color{gre}#1}}
\definecolor{red}{rgb}{0.5,0.0,0}
\def\red#1{{\color{red}#1}}
\def\norm#1{\|#1\|}
%%% End for Colours

\bracketedpoints

\makeatletter
\renewenvironment{solution}{\leavevmode\par\begin{soln}\noindent Solution:}{\end{soln}}
\makeatother
      \newif\ifsolutions\solutionsfalse

\author{}
\date{}
\title{CPSC 320 2025S: Assignment 1}

\begin{document}

\maketitle
\vspace{-0.5in} This assignment is due \textbf{Friday, July 11 at 7 PM}. Late submissions will not be accepted. Please follow these guidelines:
\begin{itemize}
	\item Prepare your  solution using \LaTeX \ and submit  a pdf file. Easiest will be to submit using
	      the .tex file provided. For questions where you  need to select a circle, you can simply
	      change \verb~\fillinMCmath~ to \verb~\fillinMCmathsoln~ .

	\item Enclose each paragraph of your solution with
	      \verb~\begin{soln}Your solution here...\end{soln}~.
	      \begin{soln}Your  solution will  then appear  in dark  blue\end{soln}, making  it a  lot
	      easier for TAs to find what you wrote.

	\item   Submit   the    assignment   via   \href{https://gradescope.ca/}{GradeScope}. You will be get access to Gradescope on the 9th of July via an invite link. Your group must make  a \textbf{single} submission via one
	      group member's account, marking all other group members in that submission \textbf{using
		      GradeScope's interface}.

	\item  After uploading  to  Gradescope, link  each  question  with the  page  of your  pdf
	      containing your solution.
\end{itemize}

Before we  begin, a few  notes on pseudocode throughout  CPSC 320: Your  pseudocode should
communicate your algorithm  clearly, concisely, correctly, and  without irrelevant detail.
Reasonable use  of plain  English is  fine in  such pseudocode.  You should  envision your
audience as a capable CPSC 320 student unfamiliar with the problem you are solving. You may \textbf{neither} include what we consider to be irrelevant coding details \textbf{nor} assume that  we understand the particular  language you
chose. (So, for example,  do not write \texttt{\#include <iostream>} at  the start of your
pseudocode,   and    avoid   language-specific   notation   like    C/C++/Java's   ternary
(question-mark-colon) operator.)

Remember also  to \textbf{justify/explain  your answers}. We  understand that  gauging how
much  justification to  provide can  be tricky.  Inevitably, judgment  is applied  by both
student and  grader as to how  much is enough, or  too much, and it's  frustrating for all
concerned  when judgments  don't align.  Justifications/explanations need  not be  long or
formal, but  should be  clear and  specific (referring  back to  lines of  pseudocode, for
example). Proofs should be a bit more formal.

On the  plus side, if  you choose an  incorrect answer when  selecting an option  but your
reasoning shows partial  understanding, you might get more marks  than if no justification
is provided. And  the effort you expend  in writing down the  justification will hopefully
help you gain deeper  understanding and may well help you converge  to the right selection
:).

\vspace{.1in}

Ok, time to get started...

\clearpage

\section*{Group Members}

Please list the CWLs of all group members here (even if you are submitting by yourself). We will deduct a mark if this is incorrect or missing.

- Jason Mac

\input{q1.tex}
\ifsolutions\else\newpage\fi

\begin{soln}
	The statement is false. Take \(n = 2\) and we construct the following SMP instance of \(2\) employees and applicants denoted by
	\(E = \{e_1, e_2\}\) and \(A = \{a_1, a_2\}\) respectively. We define this instance through the following preference lists:

	\begin{itemize}
		\item \(a_1 : e_1, e_2\)
		\item \(a_2 : e_2, e_1\)
		\item \(e_1 : a_2, a_1\)
		\item \(e_2 : a_1, a_2\)
	\end{itemize}

	We have that a stable matching can be found through the pairings, \((e_1, a_1), (e_2, a_2)\), but also with \((e_1, a_2), (e_2, a_1)\).

	Now, for each \(n > 2\), we construct a new instance through the following:

	\begin{itemize}
		\item \(a_1 : e_1, e_2, \dots\)
		\item \(a_2 : e_2, e_1, \dots\)
		\item \(a_i : e_i, \dots\)
		\item \(e_1 : a_2, a_1, \dots\)
		\item \(e_2 : a_1, a_2, \dots\)
		\item \(e_i : a_i, \dots\)
	\end{itemize}

	for \(i \in \{3, 4, \dots, n\}\), and where the permutation of the preference list does not matter except for the specified entry.

	Then we have the two following stable matchings for such an instance:

	\(S_1 = \{(e_i, a_i) : i = 3, 4, \dots, n\} \cup \{(e_1, a_1), (e_2, a_2)\}\), and

	\(S_2 = \{(e_i, a_i) : i = 3, 4, \dots, n\} \cup \{(e_1, a_2), (e_2, a_1)\}\).

	We never have an instability since by construction, for \(3 \leq i \leq n\), \(e_i\) always prefers \(a_i\) over anyone else and vice versa.

	In other words, not every instance for \(n \geq 2\) will have exactly one stable matching, but there always exists at least one by \(G-S\) algorithm.



\end{soln}


\input{q2.tex}
\ifsolutions\else\newpage\fi



\begin{soln}
	This statement is never true.

	Let \(n \geq 2\), suppose we are given an instance an SMP. Denote set of employees by \(E\) and applicants by \(A\).
	We assume for the sake of contradiction, there exists a matching \(M\) such that nobody gets their first choice.
	Then in the G-S algorithm, this implies that for each \(e \in E\) they are either rejected on their first offer or
	their applicant to which they made their first offer to is poached by someone else.

	We also observe that the top choices of each employer is not unique, otherwise each employer would have never have been rejected in their first choice and our assumption is false.
	Then we have that there exists \(e_1, e_2 \in E\) such that their top choice of applicant is some \(a \in A\).
	Observe that the top employer for \(a\) cannot be \(e_1\) or \(e_2\) since this would mean that either \(e_1\) or \(e_2\) is never rejected by \(a\) or have \(a\) stolen from them.

	Thus, the top employer choice for \(a\) is some \(e \in E\).



\end{soln}

\input{q3.tex}
\ifsolutions\else\newpage\fi

\input{q4.tex}
\ifsolutions\else\newpage\fi
\end{document}
