\documentclass[11pt,fleqn]{exam}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fancyvrb}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{algpseudocode}
\usepackage{comment}
\usepackage{enumitem}
\usepackage{ulem}
\usepackage[margin=0.75in]{geometry}
\usepackage{tikz}
\usetikzlibrary{arrows,arrows.meta,positioning,intersections,shapes.gates.logic.US,calc}
\algnewcommand\algorithmicforeach{\textbf{for each}}
\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
\newcommand{\fillinMCmath}[1]{\begin{tikzpicture}\draw circle [radius=0.5em];\end{tikzpicture}\ #1}
\newcommand{\fillinMCmathsoln}[1]{\begin{tikzpicture}\draw[black, fill=blue] circle [radius=0.5em];\end{tikzpicture}\ #1}
\newcommand{\ptsamt}[1]{[#1~points]}
\newcommand{\ptamt}[1]{[#1~point]}

%%% Adding Colour to Questions and Answers
\usepackage{color}

\definecolor{solnblue}{rgb}{0,0,1}
\newenvironment{soln}{\color{solnblue}}{}

%Questions

% Answers
\definecolor{blu}{rgb}{0,0,0.5}
\def\blu#1{{\color{blu}#1}}
\definecolor{gre}{rgb}{0,.3,0}
\def\gre#1{{\color{gre}#1}}
\definecolor{red}{rgb}{0.5,0.0,0}
\def\red#1{{\color{red}#1}}
\def\norm#1{\|#1\|}
%%% End for Colours

%fancyvrb commands
\def\lar{$\leftarrow$}
\def\lesseq{$\leq$}

\bracketedpoints

\makeatletter
\renewenvironment{solution}{\leavevmode\par\begin{soln}\noindent Solution:}{\end{soln}}
\makeatother
      \newif\ifsolutions\solutionsfalse

\author{}
\date{}
\title{CPSC 320 2025S: Assignment 3}

\begin{document}
	
	\maketitle
	\vspace{-0.5in} This assignment is due \textbf{Friday, July 25 at 7 PM}. Late submissions will not be accepted. Please follow these guidelines:
	\begin{itemize}
		\item Prepare your  solution using \LaTeX and submit  a pdf file. Easiest will be to submit using
		the .tex file provided. For questions where you  need to select a circle, you can simply
		change \verb~\fillinMCmath~ to \verb~\fillinMCmathsoln~ .
		
		\item Enclose each paragraph of your solution with
		\verb~\begin{soln}Your solution here...\end{soln}~.
		\begin{soln}Your  solution will  then appear  in dark  blue\end{soln}, making  it a  lot
		easier for TAs to find what you wrote.
		
		\item   Submit   the    assignment   via   \href{https://gradescope.ca/}{GradeScope}. Your group must make  a \textbf{single} submission via one
		group member's account, marking all other group members in that submission \textbf{using
			GradeScope's interface}.
		
		\item  After uploading  to  Gradescope, link  each  question  with the  page  of your  pdf
		containing your solution.
	\end{itemize}

\begin{quote}
 \textbf{SPECIAL NOTE ON GRADING FOR THIS ASSIGNMENT:} this assignment has two questions, each worth 12 points. If $m$ is the number of points your assignment earns out of 24, your grade for this assignment will be given by $\min\{m/12, 1\}$. (That is, earning full credit on one question, or at least 12 points combined on both questions, will earn you 100\% on the assignment.) In addition, if you earn at least 8/12 on \textbf{both} questions, we will add 3 bonus percentage points to your midterm exam grade. Also, note that \textbf{the material covered on this assignment is within the scope of midterm exam coverage}, so it is worth your time to put in some effort on these questions (even if you don't complete them) before the exam!
 \end{quote}
	
	Before we  begin, a few  notes on pseudocode throughout  CPSC 320: Your  pseudocode should
	communicate your algorithm  clearly, concisely, correctly, and  without irrelevant detail.
	Reasonable use  of plain  English is  fine in  such pseudocode.  You should  envision your
	audience as a capable CPSC 320 student unfamiliar with the problem you are solving. You may \textbf{neither} include what we consider to be irrelevant coding details \textbf{nor} assume that  we understand the particular  language you
	chose. (So, for example,  do not write \texttt{\#include <iostream>} at  the start of your
	pseudocode,   and    avoid   language-specific   notation   like    C/C++/Java's   ternary
	(question-mark-colon) operator.)
	
	Remember also  to \textbf{justify/explain  your answers}. We  understand that  gauging how
	much  justification to  provide can  be tricky.  Inevitably, judgment  is applied  by both
	student and  grader as to how  much is enough, or  too much, and it's  frustrating for all
	concerned  when judgments  don't align.  Justifications/explanations need  not be  long or
	formal, but  should be  clear and  specific (referring  back to  lines of  pseudocode, for
	example). Proofs should be a bit more formal.
	
	On the  plus side, if  you choose an  incorrect answer when  selecting an option  but your
	reasoning shows partial  understanding, you might get more marks  than if no justification
	is provided. And  the effort you expend  in writing down the  justification will hopefully
	help you gain deeper  understanding and may well help you converge  to the right selection
	:).
	
	\vspace{.1in}
	
	Ok, time to get started...
	
	\clearpage
	
	\section*{Group Members}
	
	Please list the CWLs of all group members here (even if you are submitting by yourself). We will deduct a mark if this is incorrect or missing.
	
	\input{q2.tex}
	\ifsolutions\else\newpage\fi
	
	\input{q3.tex}

\end{document}