\section{D + C = Profit}

You own an online sales company called DCAuctions.com that sells goods both on auction and on a fixed-price basis. You want to use historical auction data to investigate your fixed price choices.
	
	Over $n$ minutes, you have a good's price in each minute of the auction. You want to find the largest \textit{price-over-time stretch} in your data. That is, given an array $A$ of $n$ price points, you want to find the largest possible value of
	$$
	f(i,d) = d \cdot \min(A[i], A[i+1], \ldots, A[i+d-1]),
	$$
	where $i$ is the index of the left end of a stretch of minutes, $d$ is the duration (number of minutes) of the stretch, and the function $f$ computes the duration times the minimum price over that period. (Prices are positive, $d \ge 0$, and for all values of $i$, $f(i,0) = 0$ and $f(i,1) = A[i]$.)
	
	For example, the best stretch is underlined in the following price array: $[8, 2, \uline{9, 5, 6, 5}, 3, 1]$. Using 1-based indexing, the value for this optimal stretch starting at index 3 and running for 4 minutes is $f(3,4) = 4 \cdot \min(9,5,6,5) = 4 \cdot 5 = 20$.

 \begin{questions}
    \question[2] Describe a polynomial-time brute force algorithm to solve this problem.

    \ifsolutions\input{q3a-sol.tex}\fi 
 
     \question[1] Suppose the minimum element in $A$ is $A[k]=4$, and suppose that $A$ has length $n$. What's the best price stretch for all intervals that include $A[k]$? Briefly justify your answer.

     \ifsolutions\input{q3b-sol.tex}\fi 

     \question[5] Using the insight from the previous question, give an efficient algorithm to find the best price stretch.

     \ifsolutions\input{q3c-sol.tex}\fi 

     \question[2] Give and briefly justify a good asymptotic bound on the \textbf{worst-case} runtime of your algorithm.

     \ifsolutions\input{q3d-sol.tex}\fi 

     \question[2] Give and briefly justify a good asymptotic bound on the \textbf{average-case} runtime of your algorithm.

     \ifsolutions\input{q3e-sol.tex}\fi 
     
 \end{questions}